A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

Figure~\ref{fig:PermFields} compares the permeability distribution for all the models. As indicated in the figure's caption, the permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)). Additionally, Fig.~\ref{fig:PermFields}(b) to (f) show the cases without the element edges which discretize the domain.

This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and PCA-LinReg cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous. Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the PCA-LinReg Case give a better representation of the BaseCase. An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability distribution. Whereas, for the PDFCase and the PCA-LinReg Case, the permeability field will change if the upgrid resolution changes.

>>>>

Figure~\ref{fig:PermFields} shows permeability distribution for all cases and highlights homogeneous representation resulting from arithmetic and harmonic averaged, Figs.~\ref{fig:PermFields}c-d, whereas PDFCase and PCA-LinReg cases (Figs.~\ref{fig:PermFields}e-f) are inherently heterogeneous. Given that the BaseCase is also heterogeneous, it can be stated that models for the PDFCase and PCA-LinReg Case give a qualitatively better representation of the permeability dataset within the BaseCase. An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the coarsening has no influence on the resulting permeability distribution. However, in both, PDFCase and PCA-LinReg Case, permeability distribution will change as mesh resolution is reduced.
